A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Sell thin-stack a bit..

@@

\subsection{Step time}

>>>>

This stack representation requires substantially less space. It stores each element involved in the feedforward computation exactly once, meaning that this representation can still support efficient backpropagation. Furthermore, all of the updates to $S$ and $Q$ can be performed in-place on a GPU. These features allow this stack model to run efficiently on a GPU. We describe speed results in Section~\ref{sec:speed}.

@@

\subsection{Runtime performance}
\label{sec:speed}
